On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-17 Manuscript/manuscript.tex
small change in press summary

\section*{Press Summary}
\label{sec:press}
This simulation study evaluates the sample size necessary to estimate the mean,
standard deviation, and lag-1 autocorrelation of a stationary time series using
different block bootstrap confidence interval types. The results showed that 
percentile-based confidence intervals for the lag-1 autocorrelation may suffer 
from coverage deterioration as 
sample size is increased, motivating the authors to propose a new recentered percentile 
confidence interval which does not deteriorate in performance for greater sample sizes.
The results also suggest that when using Student's $t$ bootstrap confidence intervals, 
a sample size of at least 1600 may be sufficient to estimate the mean, 
whereas a sample size larger than 3200 may be necessary to estimate 
the standard deviation. Finally, to estimate the lag-1 autocorrelation, using
Student's $t$ bootstrap confidence intervals demands a sample size of at least 100 
when the marginal distribution is standard normal and a sample size of at least 1600 when
the marginal distribution is unit exponential.

>>>>

\section*{Press Summary}
\label{sec:press}
This simulation study evaluates the sample size necessary to estimate the mean,
standard deviation, and lag-1 autocorrelation of a stationary time series using
different block bootstrap confidence interval types. The results showed that 
percentile-based confidence intervals for the lag-1 autocorrelation may suffer 
from coverage deterioration as 
sample size is increased, motivating the authors to propose a new recentered percentile 
confidence interval which does not deteriorate in performance for greater sample sizes.
The results also suggest that when using Student's $t$ bootstrap confidence intervals, 
a sample size of at least 1600 may be sufficient to estimate the mean, 
whereas a sample size larger than 3200 may be necessary to estimate 
the standard deviation. The results additionally indicate that 
estimation of the lag-1 autocorrelation - using
Student's $t$ bootstrap confidence intervals - demands a sample size of at least 100 
when the marginal distribution is standard normal and a sample size of at least 1600 
when the marginal distribution is unit exponential.
